A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-10-01 manuscript.Rmd
minor rewording

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/workflow-showcase.git
# (2) enter the directory containing the project
cd workflow-showcase
# (3) build the docker container
make build
# (4) run the analysis and produce the final PDF inside the container
make all DOCKER=TRUE
```

>>>>

# (1) obtain a local copy of the remote repository
git clone https://github.com/aaronpeikert/workflow-showcase.git
# (2) enter the project directory 
cd workflow-showcase
# (3) build the docker container
make build
# (4) run the analysis and produce the final PDF inside the container
make all DOCKER=TRUE
```
